### 2017-09-30 TF-vldb2018/sec-dynamicTopk.tex

%\vspace{-0.5ex}
\stitle{(3) Algorithm \inc}. We now provide a unified incremental solution to handle both pattern and data updates.

Given pattern $P$ with its $h$-fragmentation ${\cal P}_{h}$, data graph $G$, two integers $r$ and $k$,
and auxiliary structures (to be introduced in Section \ref{sec-IncAlg}) such as the partial match relations for all pattern fragments and all balls (radius $r$),
the algorithm consists of three steps for $\Delta P$ and $\Delta G$, as follows.

>>>>

%\vspace{-0.5ex}
\stitle{(3) Algorithm framework}. We now provide a unified incremental algorithm to handle both pattern and data updates,
based on pattern fragmentation and affected balls.

Given pattern $P$ with its $h$-fragmentation ${\cal P}_{h}$, data graph $G$, two integers $r$ and $k$,
and auxiliary structures (to be introduced in Section \ref{sec-IncAlg}) such as the partial match relations for all pattern fragments and all balls (radius $r$),
algorithm \inc  consists of three steps for $\Delta P$ and $\Delta G$, as follows.
